uncontrolled

### 2021-02-10 inst/examples/corporate.Rmd
da

---
title: "corporate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "corporate"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$corporate))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/corporate_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$corporate))` / `r nrow(df)` (`r round(100*mean(!is.na(df$corporate)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$corporate)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$corporate)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "corporate", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$corporate)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/holder.Rmd
change
da

---
title: "corporate"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "holder"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$holder))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/holder_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$holder))` / `r nrow(df)` (`r round(100*mean(!is.na(df$holder)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$holder))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$holder)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "holder", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$holder)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/note_510c.Rmd
change
da

---
title: "holder"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "note_510c"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_510c))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_510c_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$note_510c))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_510c)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$note_510c)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_510c)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "note_510c", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$note_510c)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/note_granter.Rmd
da

---
title: "note_granter"
output: md_document
---
* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)

>>>>

---
title: "note_granter"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$note_granter))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/note_granter_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$note_granter))` / `r nrow(df)` (`r round(100*mean(!is.na(df$note_granter)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$note_granter))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$note_granter)), 1)`%)

### 2021-02-10 inst/examples/subject_topic.Rmd
change
da

---
title: "note_510c"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "subject_topic"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$subject_topic))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/subject_topic_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$subject_topic))` / `r nrow(df)` (`r round(100*mean(!is.na(df$subject_topic)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$subject_topic)` / `r nrow(df)` documents (`r round(100*mean(is.na(df$subject_topic)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "subject_topic", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$subject_topic)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/successor.Rmd
change
da

---
title: "subject_topic"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "successor"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$successor))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/successor_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$successor))` / `r nrow(df)` (`r round(100*mean(!is.na(df$successor)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$successor))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$successor)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "successor", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$successor)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```

### 2021-02-10 inst/examples/uncontrolled.Rmd
change
da

---
title: "successor"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "uncontrolled"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path=paste0("figure/rmd_", field, "_"))
```

* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$uncontrolled))`
* [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/uncontrolled_discarded.csv")) - 1)` 
* Original documents with non-NA titles: `r sum(!is.na(df$uncontrolled))` / `r nrow(df)` (`r round(100*mean(!is.na(df$uncontrolled)), 1)`%)
* Original documents with missing (NA) titles `r sum(is.na(df$uncontrolled))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$uncontrolled)), 1)`%)

 Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "uncontrolled", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```

Frequency of unique titles:

```{r uniquetitles, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
tab <- table(df$uncontrolled)
d <- data.frame(title = names(tab), n = as.numeric(tab))

library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- ggplot(d, aes(x = n)) +
  geom_histogram(color="black", fill="white") +
  scale_x_log10() +
  scale_y_log10() +
  labs(x = "Title duplicates (n)", y = "Documents (n)")
print(p)
```
